\documentclass[appendix.tex]{subfiles}

\begin{document}
Alright, so my main questions surround what factors you actually want to actually go into it.
Uhh, the current ones---I've just written up a quick version---the current one's that go into it are gender diversity, grade diversity, and having the teacher in the advisory.
Are there any other factors that you want to go into it?

Umm, right now there are no additional factors that I want to go into it.
Student Council was supposed to figure out at this morning's meeting are there any other parameters for next year that they want to go into it.
I'd say right now just try to be flexible, potentially try to consider student requests, though I'd say that's probably on the lower end of the priority scale.
You also want to have some function where you can exclude.
So sometimes there are kids that you just don't want in the same advisories.
Whether they have had something between them, or are siblings, or just spend too much time together, it is important to be able to keep some kids apart.
And I think having a system that also allows you to move kids around, but as you move kids it also gives you, if you move this kid then this kid needs to move here.
I don't know how capable that is, but the capacity to, as you move and change the equation, that there is a kind of self-correcting aspect where it says \enqueue{I you move this kid, this kid needs to go here}.
And if it can in some way show me the options that fit into the parameters without causing a larger domino effect.

Okay, then, also with teachers, I know there is a lot that goes into the pairings.
\end{document}
